Model_CFU

### 2016-12-07 Projects/HumanCdGF_cdiff_colonization.Rmd
all correlation plots for top 12 otus

set.seed(seed)
cfu_all_rf <- randomForest(cfu_all_shared_df[ , -1], cfu_all_shared_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features <- head(sort(importance(cfu_all_rf)[,1],decreasing = T), n_features)
feat_cor_cfu <- sort(abs(cor(cfu_all_shared_df[ , c('log_cfu_med', 
                                                    names(top_features))],
                             method = 'spearman')[,'log_cfu_med']),
                     decreasing = T)
```

@@

@@

set.seed(seed)
source_all_rf <- randomForest(source_all_shared_df[ , -1], source_all_shared_df$human_source,
                           ntree = 501,
                           mtry = 15,
                           importance = T)
top_features_src <- head(sort(importance(source_all_rf)[,1],decreasing = T), n_features)
#any(names(top_features) %in% names(top_features_src))
src_feat_cor_cfu <- sort(abs(cor(cfu_all_shared_df[ , c('log_cfu_med', 
                                                        names(top_features_src))], 
                                 method = 'spearman')[,'log_cfu_med']), 
                         decreasing = T)
```

@@

@@

#### Predictive OTUs that correlate with CFU  
The following predictive OTUs correlate with CFU (Spearman's _rho_ > 0.5)

Colonization Level  
`r names(feat_cor_cfu)[feat_cor_cfu>0.5 & feat_cor_cfu < 1]`

```{r plot colonization otu correlations, fig.width=10, fig.height=18}
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", names(head(top_features,12)))) %>% 
  gather(OTU, abundance, contains('Otu')) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~OTU, ncol = 4, scales = 'free_x') + scale_x_log10()
```

Inocula Source  
`r names(src_feat_cor_cfu)[src_feat_cor_cfu>0.5 & src_feat_cor_cfu < 1]`

```{r plot source otu correlations, fig.width=7.5, fig.height=3}
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", names(src_feat_cor_cfu)[src_feat_cor_cfu>0.5 & src_feat_cor_cfu < 1])) %>% 
  gather(OTU, abundance, contains('Otu')) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~OTU, ncol = 3, scales = 'free_x')
```

>>>>

set.seed(seed)
cfu_all_rf <- randomForest(cfu_all_shared_df[ , -1], cfu_all_shared_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features <- head(sort(importance(cfu_all_rf)[,1],decreasing = T), n_features)
feat_cor_cfu <- cor(cfu_all_shared_df[ , c('log_cfu_med', 
                                           names(top_features))],
                    method = 'spearman')[-1,'log_cfu_med']
```

@@

```{r plot colonization otu correlations, fig.width=10, fig.height=10}
top_n_otus <- get_tax(row_list = names(head(top_features,12)))
top_n_otus$cor_label <- paste0(top_n_otus$tax, '(OTU',
                           gsub('Otu0*', '', rownames(top_n_otus)),
                           ';rho=', round(feat_cor_cfu[names(feat_cor_cfu) 
                                                       %in% rownames(top_n_otus)], 
                                          2), ')')
top_n_otus$cor_label <- factor(top_n_otus$cor_label,
                               levels = top_n_otus$cor_label[order(head(top_features,12),
                                                                   decreasing = T)])
top_n_otus$OTU <- rownames(top_n_otus)
subset(cfu_all_shared_df, select = 
       c("log_cfu_med", rownames(top_n_otus))) %>% 
  gather(OTU, abundance, contains('Otu')) %>%
  left_join(top_n_otus) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~cor_label, ncol = 4, scales = 'free_x') + 
    labs(x= 'Relative Abundance - Day 0 (log %)', y = 'Observed Colonization (log CFU)') + 
    ylim(5, 9) + scale_x_log10(breaks = c(0, 0.01, 0.1, 1, 10, 100)) +
    theme(strip.background = element_rect(colour=NULL, fill='white'),
          panel.background = element_rect(linetype = 1, size = 1, fill = 'white', color = 'black'),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.x = element_line(linetype = 1, size = .1, color = 'gray'),
          panel.grid.minor.x = element_line(linetype = 1, size = .1, color = 'gray'))
```

***

@@

set.seed(seed)
source_all_rf <- randomForest(source_all_shared_df[ , -1], source_all_shared_df$human_source,
                           ntree = 501,
                           mtry = 15,
                           importance = T)
top_features_src <- head(sort(importance(source_all_rf)[,1],decreasing = T), n_features)
#any(names(top_features) %in% names(top_features_src))
src_feat_cor_cfu <- cor(cfu_all_shared_df[ , c('log_cfu_med', 
                                               names(top_features_src))], 
                        method = 'spearman')[-1,'log_cfu_med']
```

@@

```{r plot source otu correlations, fig.width=10, fig.height=10}
top_n_otus_src <- get_tax(row_list = names(head(top_features_src,12)))
top_n_otus_src$cor_label <- paste0(top_n_otus_src$tax, '(OTU',
                           gsub('Otu0*', '', rownames(top_n_otus_src)),
                           ';rho=', round(src_feat_cor_cfu[names(src_feat_cor_cfu) 
                                                       %in% rownames(top_n_otus_src)], 
                                          2), ')')
top_n_otus_src$OTU <- rownames(top_n_otus_src)
top_n_otus_src$cor_label <- factor(top_n_otus_src$cor_label,
                               levels = top_n_otus_src$cor_label[order(head(top_features_src,12),
                                                                   decreasing = T)])

subset(cfu_all_shared_df, select = 
       c("log_cfu_med", rownames(top_n_otus_src))) %>% 
  gather(OTU, abundance, contains('Otu')) %>%
  left_join(top_n_otus_src) %>% 
  ggplot(aes(x = abundance, y = log_cfu_med)) + geom_point() + 
    facet_wrap(~cor_label, ncol = 4, scales = 'free_x') +  
    labs(x= 'Relative Abundance - Day 0 (log %)', y = 'Observed Colonization (log CFU)') + 
    ylim(5, 9) + scale_x_log10(breaks = c(0, 0.01, 0.1, 1, 10, 100)) +
    theme(strip.background = element_rect(colour=NULL, fill='white'),
          panel.background = element_rect(linetype = 1, size = 1, fill = 'white', color = 'black'),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.x = element_line(linetype = 1, size = .1, color = 'gray'),
          panel.grid.minor.x = element_line(linetype = 1, size = .1, color = 'gray'))
```

***

@@
